---
title: "muSuSiE-graph-multi"
output: html_document
date: "`r Sys.Date()`"
---

## Generate random data

```{r}
## define parameters
p <- 100
n1 <- 300
n2 <- 400
p_c <- 100
p_1 <- 30
p_2 <- 25
sigma <- 1
sigma0 <- 0.6
A1 <- matrix(0, nrow = p, ncol = p)
A2 <- matrix(0, nrow = p, ncol = p)
set.seed(2021)
# Define the true graph given order
index_c <- sample(seq_len(p * (p - 1) / 2), size = p_c, replace = FALSE)
index_1 <- sample(setdiff(seq_len(p * (p - 1) / 2), index_c), size = p_1, replace = FALSE)
index_2 <- sample(setdiff(seq_len(p * (p - 1) / 2), index_c), size = p_2, replace = FALSE)

A1[lower.tri(A1)][c(index_c, index_1)] <-  rnorm(p_c + p_1, mean = 0, sd = sigma0)
A2[lower.tri(A2)][c(index_c, index_2)] <-  rnorm(p_c + p_2, mean = 0, sd = sigma0)

alpha_mat_1 <- matrix(0, nrow = p, ncol = p)
alpha_mat_1[lower.tri(alpha_mat_1)][c(index_c, index_1)] <- 1
alpha_mat_2 <- matrix(0, nrow = p, ncol = p)
alpha_mat_2[lower.tri(alpha_mat_2)][c(index_c, index_2)] <- 1

eps_1 <- matrix(rnorm(p * n1), nrow = p, ncol = n1)
dta_1 <- solve(diag(1, nrow = p) - A1, eps_1)
dta_1 <- t(dta_1)
eps_2 <- matrix(rnorm(p * n2), nrow = p, ncol = n2)
dta_2 <- solve(diag(1, nrow = p) - A2, eps_2)
dta_2 <- t(dta_2)

dta_list <- list()
dta_list[[1]] <- dta_1
dta_list[[2]] <- dta_2
```

## Get graph

For multiple data sets, we can use function **joint_graph_multi** in **muSuSiE-graph-multi.R**. Here

1. Each entries of dta_list is a n_i x p data sets, they can have different sample size but must have the same features.

2. **prior_vec:** is a vector of dimensional 2^p - 1.

3. All others are the same as the two data sets case.

```{r}
source("mutipledatasets/muSuSiE-graph-multi.R")
out_res <- joint_graph_multi(dta_list, scale_x = FALSE, intercept = TRUE,
                             sigma02_int = NULL, sigma2_int = NULL, prior_vec = NULL,
                             com_mat = NULL, com_list = NULL,
                             itermax = 100, L_max = 10, tol = 1e-4, sigma0_low_bd = 1e-8,
                             residual_variance_lowerbound = NULL)
```

## Check results

```{r}
names(out_res)
```

1. alpha_res_list: each entry is a p x p matrix, the (ij)-th entry is the probability that the edge i -> j exist.

2. A_res\_\_list: each entry is a p x p matrix, the regression coefficients.
